%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Embedded Software Developer - Autosar and core embedded} % Job title
    {TATA Elxsi limited.} % Organization
    {Bangalore} % Location
    {Sep. 2023 - Present} % Date(s)
    {
       {\textbf{Minerva : Mercedes-Benz RDI}}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \ {\textbf{      }}
        \item %{Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS ECR and Rancher.}
        \item {Implemented clock plausibility checks and UCB validation within the L3SM CDD component, integrating ZF archive library for Level 3 Safety Manager functions.}
  \item {Configured SMU and vLinkGen modules using DaVinci Configurator and Developer for ADAS applications.}
  \item {Set up additional critical AUTOSAR modules including OS, EcuM, vBaseEnv, and MCU.}
  \item {Developed ADC-based voltage failure detection logic with error reporting mechanisms.}
  \item {Implemented error precondition validation using system power state and ADAS state to ensure proper handling before raising critical DTC.}
        \item %{Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}
      \end{cvitems}
      {\textbf{FACE : Sumitomo-Nissan}}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \ {\textbf{      }}
        \item %{Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS ECR and Rancher.}
        \item {Designed and implemented Complex Device Drivers: ADC, SPI, PROFET, SPOC.}
        \item {Developed Sensor Software Components (SWC) for automotive applications.}
        \item {Executed Automotive V-flow Software Engineering processes (SWE1, SWE2, SWE3, SWE4).}
        \item {Ensured compliance with automotive safety standards like ASPICE and MISRA.}
      \end{cvitems}
    }
 
%---------------------------------------------------------
  \cventry
    {Embedded Software Developer} % Job title
    {Niagara Automations Pvt Ltd.} % Organization
    {Coimbatore,} % Location
    {Jul. 2021 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led the development of embedded systems for industrial automation and IoT applications, including RTOS-based controllers, sensor interfacing, and remote monitoring solutions.}
        \item {Designed and implemented robust communication protocols using GSM, LoRa, RS485, and MQTT for reliable device-to-cloud and device-to-user connectivity.}
        \item {Developed firmware and algorithms for process control, power factor optimization, and system fault management, enhancing system efficiency and reliability.}
        \item {Conducted end-to-end system validation, debugging, and optimization, ensuring industrial-grade performance under varying operational conditions.}
        \item {Mentored junior engineers, reviewed code and design decisions, and contributed to process improvements and documentation standards.}
      \end{cvitems}
    }

\end{cventries}
