%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Key Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {\textbf{GSM Pump Controller}} % Project
    {} % Empty role
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems}
        \item {Designed and implemented a pump controller system using Nuvoton M483 MCU with FreeRTOS.}
        \item {Implemented voltage and current sensing, motor protections, and dry-run restart timers.}
        \item {Integrated GSM functionalities including SMS, calls, FTP, DTMF, and network AT commands for reliable device-to-user communication.}
        \item {Sent system status and fault codes to an MQTT server for mobile app monitoring and control.}
      \end{cvitems}
    }

\cventry
    {\textbf{Flow and Pressure Control System}} 
    {} 
    {} 
    {} 
    {
      \begin{cvitems}
        \item {Developed control system using SAM D21 MCU to interface with multiple sensors: 4-20mA pressure sensors, RS485 level sensors, float and door switches, pulse and RS485 flowmeters.}
        \item {Controlled two solenoid coils to maintain target flow and pressure rates.Also Used EERAM to store cumulative data, calibration factors, and setpoints.Displayed parameters on a dot matrix display for real-time monitoring.}
      \end{cvitems}
    }

\cventry
    {\textbf{Oxygen Tank Level Monitoring System}} 
    {} 
    {} 
    {} 
    {
      \begin{cvitems}
        \item {Designed system to measure differential pressure from two sensors and convert readings to mmWc.}
        \item {Implemented MQTT communication to send hourly tank data to a server and Configured alerts to notify low oxygen levels.}
      \end{cvitems}
    }

\cventry
    {\textbf{LoRa Node for Remote Fluid Control}} 
    {} 
    {} 
    {} 
    {
      \begin{cvitems}
        \item {Developed LoRa-based control system to receive commands and operate solenoid coils remotely.}
        \item {Provided feedback including acknowledgements, battery, and solar voltages.}
        \item {Enabled efficient and reliable remote monitoring and control of fluid flow processes.}
      \end{cvitems}
    }

  \cventry
    {\textbf{Edge-IO Data Acquisition and Modbus TCP Device}} 
    {} 
    {} 
    {} 
    {
      \begin{cvitems}
        \item {Designed an Edge-IO device to read ADC and digital inputs and transmit raw data over Modbus TCP.}
        \item {Developed a Yocto-based application to receive Modbus TCP data and forward it via MQTT.}
        \item {Implemented using Libmodbus, cJSON, and Paho MQTT libraries, with static compilation to minimize dependencies and simplify deployment.}
      \end{cvitems}
    }

\cventry
    {\textbf{STM32F4 RTOS Scheduler (Hobby Project)}} 
    {} 
    {} 
    {} 
    {
      \begin{cvitems}
        \item {Implemented a round-robin RTOS scheduler on STM32F4 to study context switching and task management.}
        \item {Used FreeRTOS implementation as reference to understand and demonstrate task scheduling on ARM Cortex-M MCU.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
